
\section{Model simplifications}
Robots communicating with other robots should be done through the control station. Dismisses issues when many robots try and work out a situation. Should be the only point of connection between rovers? Used to identify other rover obstacles?

Simplify through making the calculation of the strategy done in the control station? Different strategy options? (Could potentially break our one algorithm down into a few different ones that each deals with one separate strategy)

Simplify the robot by doing the calculation of strategies in the control station. "Assign" mission in station and calculate it THEN send it to the robot for execution of navigation?

Strategy could be any type of pathing.

The reward points should be a total, each robot does not have a separate score.

Change the use case diagram as strategies now are decided by the control station

Change use-case diagram by removing the include relation between the navigate to point and the calculate strategy.

Generalize "Assign mission" use case to include all event transmissions from control station to the robot.

Reward procedures should be changed to only be used by the control station now that the strategies are calculated there instead of in the robot.



\section{System responsibility breakdown}
\subsection{Robot}
The robot has to be able to execute the latest strategy without being connected to the control station. 

\subsection{Control Station}
Stores some information. Elementary calculations

\subsection{Interface}









\section*{Supervision notes}
Looks like a networking device is communicating between many network devices

Our choice if we want the robot to care about points or not (Wi-Fi down) etc

Drop "execute strategy" from "calculate" strategy

Clarify that emergency stop is part of assign mission..? (Generalize to Assign Event?)

Decompose the different use cases

Sergio? (Simulator Questions)
