

\subsection*{Social Contract}

\subsubsection*{Responsibilities of Each Group Member}
Each group member is responsible to...
\begin{enumerate}
    \item do as well as they can.
    \item attend meetings regularly, and on time. If they are late to a meeting, they're responsible for bringing fika for everyone to the next one.
    \item keep track of the communication, by checking the slack workspace at least once a day, on work days.
    \item pay close attention during meetings, and keep distractions to a minimum.
    \item ask for help, if they face any difficulties. The responsibility to admit they're having difficulties is on them alone.
    \item keep a positive attitude towards the team work. 
    \item address conflicts with or within the team as quickly as possible, if they occur.
\end{enumerate}


\subsubsection*{Expectations for the Course}
\begin{enumerate}
    \item The team has agreed, that we do not aim for a particular grade, but instead wish to maximize our learning experience, spend our time concentrated on our work and do our overall best.
    \item The team also puts a cap on our hours we want to spend at 15 to 20 hours per week.
    \item A priority is to keep the workload even, while still aiming for everyone to put their best foot forward.
    \item The group is responsible for keeping all group members up to date on the progress.
    \item It's important that all members feel responsible within the group, and like their contributions are of value to the overall work. It's also important that everyone contributes to the project.
\end{enumerate}

% A definition of the responsibilities of a team member.
% The goals and objectives of the team.
