\begin{enumerate}
\item Social contract
\item Domain model breakdown
\begin{itemize}
\item Use cases with responsible and controller
\item 
\end{itemize}
\end{enumerate}

\section{Social contract and Responsibilities}
\begin{enumerate}
    \item Ambition
    \item Late/no show for meeting (Serve fika)
    \item Check chat once a weekday
    \item Attention during meetings
    \item Ask for help
    \item Keep a positive attitude
    \item How we solve conflicts
\end{enumerate}

\section{Goals and Objectives}
\begin{enumerate}
    \item We are not aiming for a certain grade, instead our goal is to spend the time we plan and do our best.
    \item Spend 15-20 hours per week on the course
    \item Doing the best work we can while keeping workload even
    \item Follow agreed on group work and meeting plan
    \item All members should be kept up-to-date on our progress
    \item All members should feel they have responsibility and are contributing to the project
\end{enumerate}

\section{Domain model}

Comments: \begin{enumerate}
    \item We consider Rovers to be instances of Robots
    \item Sensors and actuators are parts of a robot
    \item The environment is sort of the whole model, so in a way everything is connected to it (Could be converted to Area and removed)
    \item Operators (both technical and non-technical) are humans that can interact with the system through the interface of the central station. In our domain, they classify as actors and therefore are not part of the domain model itself.
    \item Missions and robots can coupled by an assignment (Not defined whether or not a mission owns a mission or the other way around)
    \item Networking device - Connects the central station and the robot.
    \item Reward points are stored/calculated in the central station for each robot according to the procedure as well as robot location.
    \item The reward procedure (A and B) decides how points are rewarded and is updated over time.
    \item The time for rewarding points isn't modelled in the domain model but is something handled by a specific part of the system which relays the current timer from a central point.
	\item Obstacles entail both static and dynamic physical objects which are present within the environment and its areas.
\end{enumerate} 

NOTE: Check aggregation and so forth with networking devices, sensors, and actuators.
Words left: Monitor

\begin {enumerate}
\item Obstacle Avoidance
\item Obstacle Identification
\item Navigate to Point PRIO Snezhina                   Controller: Victor
\item Calculate Strategy PRIO Victor                    Controller: Sebastian
\item Execute Strategy 
\item Event Assignment PRIO Sebastian                   Controller: William
\item Mission Assignment
\item Update procedure PRIO Philip                      Controller: Svante
\item Display Position
\item Reward Points and Update interface PRIO Svante    Controller: Snezhina
\item Display Camera 
\item Robot fault PRIO William                          Controller: Philip
\end{enumerate}